Top Private Equity Firms with Larger Average Fund Sizes and Lower Internal Rate of Returns (IRRs) in the United States Give ESG a Higher Importance

### 2024-04-18 paper/paper.qmd
Stimulate and Test Data
Updated the scripts to stimulate and test the datasets

@@

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

>>>>

The estimand for this paper is the effect of various firm-specific factors (Total Number of Funds, Fund Size, IRR, Staff Count, and Average Fund Size) on a private equity firm's ESG scores.

@@

## Findings and Comparison

The results from the negative binomial regression model provide insights into the factors influencing ESG scores in private equity firms. The findings suggest that 'Total Number of Funds' and 'IRR' are positively associated with ESG scores, although with relatively modest coefficients and high standard errors. Conversely, 'Fund Size', 'Staff', and 'Average Fund Size' demonstrate negligible impact on ESG scores.

Comparing these results to PAPER, there are several similarities and differences. In the original paper, neither 'IRR (Preqin)' nor 'IRR (All)' showed significant influence on ESG scores. In contrast, this paper's results identify a positive relationship between IRR and ESG scores. This discrepancy suggests that firm performance, as measured by IRR, might indeed predict ESG activities. The original paper also considered the variables 'Log Fund Size' and 'Staff Count' as potential regressors, and found that neither variable had a statistically significant relation with a firm's ESG Score. This paper did not apply a log to the fund size, and had replaced the data for staff (instead of using Preqin's data, LinkedIn's data was used). However, despite the aforementioned changes to the data,this paper also found that neither of these two variables had a significant relation with ESG scores.

## Weaknesses

## Future Research
